A decomposition based on constrained clustering algorithms for job shop scheduling problems\thanks{Supported by organization x.}

### 2021-08-18 Artificial Intelligence and Machine Learning/PADL_conference/Paper_draft_v1.tex
adding a paper draft

\documentclass{article}
\usepackage{graphicx}
\usepackage[utf8]{inputenc}
\usepackage{todonotes}
\usepackage{textcomp}
\usepackage{color,soul}
%\usepackage{array}
%\newcolumntype{P}[1]{>{\raggedleft\arraybackslash}p{#1}}

\usepackage{geometry}
\usepackage{changepage}
%\newcolumntype{L}[1]{>{\raggedright\arraybackslash}p{#1}}
%\newcolumntype{C}[1]{>{\centering\arraybackslash}m{#1}}
\renewcommand{\baselinestretch}{1.2}

\newcommand{\comment}[1]{\todo[inline]{#1}}

\title{\textbf{A decomposition based on constrained clustering algorithms for job shop scheduling problems} \\}

\author{\\[1in] Student: \\ \textit{\textbf{Mohammed El-Kholany, MSc.}}\\Alpen-Adria-Universität Klagenfurt, Austria \\[3in] }
\date{August 2021}

\begin{document}

\clearpage\maketitle
\thispagestyle{empty}
\clearpage
\setcounter{page}{1}
\newpage
\section{Introduction}
Nowadays, the massive progress and development of the internet and online technologies, data generated by machines and devices, product development, quality and inventory management systems, or production planning systems has become huge and is expected to increase in the coming years. Hence, to capture long-term revenues and sustainable competitive advantages, companies must manage the knowledge and have the valuable information to make the right decision at the right time \cite{benabdellah2019survey}. \\

@@

Furthermore, from an optimization perspective, the main objective is to minimize the distance between objects falling in the same cluster and maximize the distance between the others that belong to different clusters. Since clustering does not use a subset of the dataset as labels to learn a classification model, clustering differs from classification \cite{wagstaff2001constrained}. In other words, with the terminology of machine learning, clustering is a form of an unsupervised task, which calculates the similarity between data objects without knowing the proper attribution~\cite{li2018geometric}. Due to these unsupervised characteristics, clustering is known as one of the most challenging machine learning tasks \cite{benabdellah2019survey}.

@@

\section{Literature Review}
In this section, we will review some of the most related works about data mining approaches employed to solve scheduling problems. Over the last decades, solving the scheduling problem has attracted the interest of many researchers, and a wide range of approaches has been developed for solving the scheduling problem. One of the approaches that have been widely used to solve the problem is data mining. The main idea of data mining is to explore the patterns from the obtained solutions by some heuristics and then develop some decision rules that approximate the order of the operations in each machine \cite{ismail2012production}. More precisely, it aims to get an order of the operations according to some characteristics.\\

@@

It can be said that the attributes of the classical JSP are quite a few and not sufficient to define the similarity and dissimilarity between the operations. The lack of these attributes guides us to extract more features that could specify which operations are similar and should be in the same window and which shall not be in the same window. The main contribution of this work is to extract some features that have a significant impact on the decomposition process and accordingly on the makespan. 
More specifically, we need to extract some features to define which operations are similar to be scheduled in the same window and get a near-optimal solution in a reasonable time.

@@

\section{Proposed Algorithm}
In this section, we will show the implementation of our proposed model and how it works. The main idea of the proposed model is to split the problem into sub-problems, solve them sequentially and integrate the solutions to have the solution of the main problem. We aim to decompose the problem into time windows because this technique proved its effectiveness for solving the scheduling problems. Several ways have been presented during the last decades to decompose the problem  \cite{zhai2014decomposition,singer2001decomposition,ovacik2012decomposition,uzsoy2000performance}.\\

@@

Figure 1 shows a flowchart of the proposed algorithm. As shown in the flowchart, the number of clusters is given. We calculate the cluster capacity by dividing the total number of operations by the number of clusters. In the next step, the clustering process started by generating the centroids, where the number of centroids is the number of clusters. In general, the centroids are generated randomly as well as in our model. However, we selected some operations as centroids. Although the operations are selected randomly, we followed a rule to select the centroids. For example, let us assume that a job consists of 15 operations, and three centroids should be generated. The first centroid will be an operation of rank 1 - 5, the second centroid will be 6 - 10, and the third will be from the last five operations. We followed this strategy to make them far from each other because the operations grouped in the first clusters should be at the beginning of their jobs. After generating the centroids, we perform a double-check for exceeding the number of clusters and the cluster capacity, respectively. After that, we calculate the distance between each operation and the centroid of the current cluster using Euclidean distance and assign the nearest operation to that cluster. In order to satisfy the precedence constraint, we check if the predecessor is not assigned to a cluster, it will be assigned to the current cluster, and the centroid is updated. If the maximum number of operations is reached, we will go to the next cluster. After assigning all operations into clusters, the algorithm terminates.

\begin{figure}[h!]
  \includegraphics[width=\linewidth]{Flow_chart_9.png}
  \caption{Flowchart of the proposed Clustering Algorithm.}
  \label{fig:Flowchart of the proposed Clustering Algorithm}
\end{figure}

@@

We neglected the rank of an operation and the time length of a job because they had negative impact results from the preliminary experiments. The following table shows the selected features, and the performance of each combination for solving benchmark instances of 50 jobs and 15 machines \cite{taillard1993benchmarks}. The following table shows the results of our experiments. The first column represents the instances we tested, and the next three columns show the makespan values obtained by FIFO, MTWR, and EST heuristics. From the fifth column, we show the makespan values obtained by combining the features mentioned above. Our experiments found that the first five combinations do not provide good solutions compared to the other heuristics. However, features (\textbf{F6}, \textbf{F8}, \textbf{F11}, \textbf{F12}, \textbf{F14} and \textbf{F15}) have a good impact in the cost function in the most cases. Especially, combinations \textbf{F6} and \textbf{F15} provided good results. It means that the most important features extracted from the problem itself and have a positive impact on the performance are \textit{Remaining Processing Time, Machine Load and Earliest Starting Time}. Also, The information obtained from the solutions of the other heuristics like (\textit{Starting Time} and \textit{Waiting Time}) led us to get better decomposition for the problem at hand. More specifically, combining \textit{Remaining Processing Time} with \textit{Machine Load} provides a good decomposition with/without \textit{Waiting Time} attributes obtained by the other heuristics.

@@

    \label{tab:table1}
 \begin{adjustwidth}{-3cm}{}

@@

\newpage
\bibliographystyle{ieeetr.bst}
\bibliography{references.bib}
\end{document}

>>>>

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.20 of 2017/10/04
%
\documentclass[runningheads]{llncs}
%
\usepackage{graphicx}
\usepackage{changepage}
\usepackage{cite}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}

\begin{document}
%
\title{A decomposition based on constrained clustering algorithms for job shop scheduling problems\thanks{Supported by organization x.}}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Mohammed M. S. El-Kholany\inst{1}\orcidID{0000-1111-2222-3333} \and
Second Author\inst{1}\orcidID{1111-2222-3333-4444} \and
Third Author\inst{1,2}\orcidID{2222--3333-4444-5555}}
%
\authorrunning{M. El-Kholany et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Alpen-Adria-Universität Klagenfurt, Klagenfurt, Austria 
\email{\{mohammed.el-kholany, konstantin.schekotihin and martin.gebser\}@aau.at}\\
%\url{http://www.springer.com/gp/computer-science/lncs} \and
Technische Universität Graz, Graz, Austria\\
\email{mgebser@ist.tugraz.at}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
Scheduling decision in production planning plays a significant role in the manufacturing industry. A good schedule may lead to solve production problems and improve productivity. Job-shop Scheduling Problem (JSP) is one of the most crucial problems in production systems. JSP deals with allocating tasks on resources and determining the sequence of the operations on each machine. The main objective of JSP is to complete the processing of all operations in a minimal time. One of the most effective approaches studied by many researchers for solving the JSP is decomposition. This work aims to apply the decomposition strategy to split the problem into a series of sub-problems using data mining methodologies. We will propose a clustering algorithm to group the data points (operations) into clusters, where each cluster is a Time Window. The decomposition process depends on two main phases; the first phase is to extract features to predict the sequence of the operations on each machine. These features are extracted either from the problem itself or from solutions obtained by other heuristics. The second phase is to develop a constrained clustering algorithm to assign each data object (an operation) into a cluster. We solved the problem using the Answer Set Programming model, and we tested our proposed algorithm on a set of benchmark instances, and the results showed that our proposed outperformed other heuristics in most cases. The results also showed that some features like \textit{Remaining Processing Time}, \textit{Machine Load} and \textit{Earliest starting Time} have a significant impact on the solution quality.

\keywords{Job-shop Scheduling  Problem \and Constrained Clustering \and Time Windows \and Answer Set Programming.}
\end{abstract}
%
%
%
\section{Introduction}
Nowadays, the massive progress and development of the internet and online technologies, data generated by machines and devices, product development, quality and inventory management systems, or production planning systems has become huge and is expected to increase in the coming years. Hence, to capture long-term revenues and sustainable competitive advantages, companies must manage the knowledge and have the valuable information to make the right decision at the right time \cite{benabdellah2019survey}. \\

@@

Furthermore, from an optimization perspective, the main objective is to minimize the distance between objects falling in the same cluster and maximize the distance between the others that belong to different clusters. Since clustering does not use a subset of the dataset as labels to learn a classification model, clustering differs from classification \cite{wagstaff2001constrained}. In other words, with the terminology of machine learning, clustering is a form of an unsupervised task, which calculates the similarity between data objects without knowing the proper attribution~\cite{li2018geometric}. Due to these unsupervised characteristics, clustering is known as one of the most challenging machine learning tasks \cite{benabdellah2019survey}. \\

@@

\section{Literature Review}

In this section, we will review some of the most related works about data mining approaches employed to solve scheduling problems. Over the last decades, solving the scheduling problem has attracted the interest of many researchers, and a wide range of approaches has been developed for solving the scheduling problem. One of the approaches that have been widely used to solve the problem is data mining. The main idea of data mining is to explore the patterns from the obtained solutions by some heuristics and then develop some decision rules that approximate the order of the operations in each machine \cite{ismail2012production}. More precisely, it aims to get an order of the operations according to some characteristics.\\

@@

It can be said that the attributes of the classical JSP are quite a few and not sufficient to define the similarity and dissimilarity between the operations. The lack of these attributes guides us to extract more features that could specify which operations are similar and should be in the same window and which shall not be in the same window. The main contribution of this work is to extract some features that have a significant impact on the decomposition process and accordingly on the makespan. 
More specifically, we need to extract some features to define which operations are similar to be scheduled in the same window and get a near-optimal solution in a reasonable time. \\

@@

\section{Proposed Algorithm}

In this section, we will show the implementation of our proposed model and how it works. The main idea of the proposed model is to split the problem into sub-problems, solve them sequentially and integrate the solutions to have the solution of the main problem. We aim to decompose the problem into time windows because this technique proved its effectiveness for solving the scheduling problems. Several ways have been presented during the last decades to decompose the problem  \cite{zhai2014decomposition,singer2001decomposition,ovacik2012decomposition,uzsoy2000performance}.\\

@@

Fig.~\ref{fig1} shows a flowchart of the proposed algorithm. As shown in the flowchart, the number of clusters is given. We calculate the cluster capacity by dividing the total number of operations by the number of clusters. In the next step, the clustering process started by generating the centroids, where the number of centroids is the number of clusters. In general, the centroids are generated randomly as well as in our model. However, we selected some operations as centroids. Although the operations are selected randomly, we followed a rule to select the centroids. For example, let us assume that a job consists of 15 operations, and three centroids should be generated. The first centroid will be an operation of rank 1 - 5, the second centroid will be 6 - 10, and the third will be from the last five operations. We followed this strategy to make them far from each other because the operations grouped in the first clusters should be at the beginning of their jobs. After generating the centroids, we perform a double-check for exceeding the number of clusters and the cluster capacity, respectively. After that, we calculate the distance between each operation and the centroid of the current cluster using Euclidean distance and assign the nearest operation to that cluster. In order to satisfy the precedence constraint, we check if the predecessor is not assigned to a cluster, it will be assigned to the current cluster, and the centroid is updated. If the maximum number of operations is reached, we will go to the next cluster. After assigning all operations into clusters, the algorithm terminates.

\begin{figure}[h!]
  \includegraphics[width=\linewidth]{Flow_chart_9.png}
  \caption{Flowchart of the proposed Clustering Algorithm.}
  \label{fig1}
\end{figure}

@@

We neglected the rank of an operation and the time length of a job because they had negative impact results from the preliminary experiments. The following Table~\ref{tab1} shows the selected features, and the performance of each combination for solving benchmark instances of 50 jobs and 15 machines \cite{taillard1993benchmarks}. The following table shows the results of our experiments. The first column represents the instances we tested, and the next three columns show the makespan values obtained by FIFO, MTWR, and EST heuristics. From the fifth column, we show the makespan values obtained by combining the features mentioned above. Our experiments found that the first five combinations do not provide good solutions compared to the other heuristics. However, features (\textbf{F6}, \textbf{F8}, \textbf{F11}, \textbf{F12}, \textbf{F14} and \textbf{F15}) have a good impact in the cost function in the most cases. Especially, combinations \textbf{F6} and \textbf{F15} provided good results. It means that the most important features extracted from the problem itself and have a positive impact on the performance are \textit{Remaining Processing Time, Machine Load and Earliest Starting Time}. Also, The information obtained from the solutions of the other heuristics like (\textit{Starting Time} and \textit{Waiting Time}) led us to get better decomposition for the problem at hand. More specifically, combining \textit{Remaining Processing Time} with \textit{Machine Load} provides a good decomposition with/without \textit{Waiting Time} attributes obtained by the other heuristics.

@@

    \label{tab1}
 \begin{adjustwidth}{-3.7cm}{}

@@

\bibliographystyle{splncs04}
\bibliography{references}

\end{document}
